\section{The Clocktower}\label{the-clocktower}

\subsubsection{A Fairy Tale Adventure}\label{a-fairy-tale-adventure}

\subsection{Flora Pizey}\label{flora-pizey}

\subsubsection{Friday 5th September
2014}\label{friday-5th-september-2014}

\chapter{Before}

\sffamily \LARGE
Once Upon a fairy tale day a girl and a boy lay down on crisp emerald
green grass, gazing up at a cool blue sky, misty clouds spread
themselves out on the picturesque scene

``Pippy, What if something happens, like something bad?''

``What do you mean Oli? \emph{Nothing} in the WHOLE WIDE WORLD can
separate us, no force known to man (or fairies) will rip us apart!''

Oli sighed and said ``Yeah, I guess so'' but something inside him felt
wrong

Oli and Pippa were bestest of friends and as Pippa had stated nothing
could tear Oli from Pippa or Pippa from Oli; or so they thought\ldots{}

The sun was setting and they needed to go to bed.

``Race you!'' Oli shouted

``You bet!'' Pippa replied, they raced through the autumn woods down the
pebbled lane and stopped at Fairy Walkway. Fairy Walkway got its name
from its arc of woven ivy and trees that curl their curious branches
around each other creating a patched and woven door way. In between the
ivy and vines beautiful flowers grew: red ones, blue ones, lilac, sunny
yellow, rosy pink and deep violet with midnight blue outer petals, some
big flowers and some tiny, just as big as your little finger nail.

They entered the small hollow and said hello to all the fairies and
pixies, the elves sat in their own group, of course. (Elves are quite
anti-social and quiet). All the fairies and pixies hovered over, their
wings glinting in the twilight.

The fairies have slim and elegant bodies you feel you could almost snap
them in half, they have beautiful faces that would take you breath away.
Pixies are also quite good looking with strong, sturdy wings and
muscular chests that shine if they catch the light, their faces are also
very muscular, they have strong, handsome features that can stop passing
fairies in their tracks. Elves however are quite grumpy looking with a
threatening scowl that is tattooed on their wrinkly faces. Even if elves
are in a relatively good mood (which they rarely are) the tattoo doesn't
wash off. This way the elves can be rather crafty, they can tell lies
like none you have ever heard!

Darkness was almost falling and they needed to have some dinner. Dinner
consisted of acorns, blackberries and maple sap for dessert. They gulped
this down in two seconds flat, it had been a long and tiring day up on
the hillside, near Ashwood Cove, no one ever went near Ashwood Cove, not
even the ogres and trolls and not \emph{even} the big trimp-tackers:
they were the biggest, fiercest, most dangerous creatures in the whole
of the world!

Pippa scrambled into bed, which was in a hollow tree in two leaves sewn
together with ivy vines to make a sleeping bag. The tree was cosy with a
lamp lit by a little glow worm in a glass jam jar.

``Night Pippi!'' Oli called from his bed in the same big old oak tree on
a branch-bunk just above Pippa's hollow.

``Night Oli!'' Pippa called in response.

Meanwhile, while Pippa nad oli were going to bed, people were waking up
somewhere not so far away on another world completely. Lots of people
lived there, normal people and a normal village . The village people
were always going about their jobs normally every single day. Some of
the folks wanted something exciting to happen for once, but it never
did.

As I said, everything was normal, except one thing, well one person. A
man and his wife lived by themselves: no baby, no child, no nothing.
This was because they couldn't. So old John spent his days searching and
searching and searching everywhere. \emph{All} the orphanages, all the
church doorsteps and asking around ``has any body seen an abandoned
girl?'' They particularly wanted a girl so she could be beautiful and
radiant and all the village to love her. she could swish her long glossy
hair and it would ripple like a rushing river in the wind, or so they
hoped.

Ring, ring, ring! ``Oh shhh'' John croaked as he fell out of his rather
dishevelled bed, went back to sleep for a minute on the floor and then
realised what the time was. ``Oh no, oh I need to get up quick!'' he
said ``Mmm grrr hoor shooo'' John's wife groaned.

John's early morning work was searching. He searched and searched but
after twelve years of searching the little village he had looked in all
the church doorsteps and scanned all the nooks and crannies for a lost
baby or a homeless girl (pretty of course); and all the orphanages. He
checked them almost every day, in the evenings, just in case any body
gave in their baby or found one.

Today though he decided to go right into the village square, where the
clocktower is. The clocktower was in the centre of the village both
literally and in their hearts. the Tower was tall, very tall; it could
almost touch the clouds! John gazed up at the top of the Tower, where
the clock face is and then looked forward, in front of him. He saw some
mini double doors! It looked like a trap door. He looked around, no one
was up yet, it was very early. John went over and yanked one open. It
was very difficult because moss had glued its soft pillowness into the
gaps forming a very effective glue. Ivy crawled its evil vines around
the door knob meaning it was extremely hard to turn, but he managed
eventually.

Inside it was pitch black, but John always carried a lamp around so he
lit the lamp and pulled the door but left it ajar. He looked right and
he saw a staircase which he guessed was the extraordinarily long one
that led right up to the top of the Clocktower. then in front of him he
saw another tiny trap door, yet it was a sort of circular door with an
indented edge, just like a cog he thought. John tugged and pulled and
yanked but the door \emph{wasn't} going anywhere. ``Maybe it was
locked?'' but there was no key hole! ``Maybe ivy and foliage blocked it
from the other side, because there certainly wasn't any on this side.''
thought John. So he kept on trying and trying until at \emph{last} with
one tremendous tug he pulled the cog door open.

On the other side it appeared to be night time. every thing was dark,
the moon shone through the magnificent trees. John assumed it was an
entirely different world, then he had an idea, he was the first person
to set foot on it. In that case he shouldn't tell any one because then
they might claim it to be theirs he thought.

As he walked through it he realised how magical it was the way the
branches creep over you like hands about to kill, the way the moon
reflects on the shimmering lake that rushes down the steep hill side.
Now John was right at the top of the hill he could see everywhere
around. At the bottom he could see a small forest with an arch of plants
for the entrance, a little pebbled path led up to it. ``That looks
nice.'' he thought. The rest of the view was stunning, he could see
forests and lakes, bushes with gorgeous looking berries and mountains
like something out of a fairytale.

John followed the narrow path, his long beard billowing in the wind. It
was dark but John came prepared, he had his lamp. He could hear little
chuckles coming from the woods and the occasional tit-ta-woo from an owl
high up in the tree tops and the tiny scuttling of squirrels or mice, or
even rabbits, sometimes he heard a crunch or a snap from a fox or badger
or some other animal.

Zz yhh grizzle as John stepped through the arc that was the fairy
walkway, he could hear odd sorts of snoring noises. ``Ahah!''thought
John. But when he stepped in to the hollow all he could see was sleeping
Fairies and Pixies, and what he guessed were Elves. He cautiously crept
up to them, they immediately turned round. They were scowling fiercely,
John didn't know whether this was normal or whether they were extremely
angry! He thought for a moment and then said anxiously ``D-d-doy-you
know of an-y git-l around h-here?'' He stammered. The Elves replied
gruffly ``Yes, in the hollow tree.'' The biggest one (he looked like the
leader) said. ``Th-th-thank you!'' he said with an element of victory
mixed with fear in his voice, for the Elves were \emph{not} very
welcoming, at all.

What he needed to find was a hollow tree, fairly big so it could fit a
human girl in. A few metres away he saw one! ``Ahah!'' he chuckled ``I
done it!'' John saw a little huddled figure in a massive oak tree making
sort-of sniffly, sleeping noises. Above her a boy lay on a branch, he
looked like he was about to fall off.

John lifted the girl, who was in fact very pretty, with long honey
coloured hair that flowed over her resting shoulders. The boy on the
branch was also rather good looking with dark treacle coloured hair and
skin like burned caramel. The girl had golden brown skin. They must
catch the sun a lot here John thought. The girl had a little gold chain
around her neck with a half love heart in the middle. On the half love
heart it said ``Oli'' and had a picture of a boy. John even though he
was getting old and his eye sight wasn't the best, could tell that that
was the boy on the branch! And just out of curiosity he tried to see
whether the boy had a chain, he did it was another half-heart and it
said ``Pippa'' with an obvious picture of the girl in his arms.

Worried that the girl, who he guessed was called Pippa, would wake up
John hurried back through the trees and over the hill, past the lake and
back where he started.

John had less heaving and pulling to do this time because the last time
he had eased the door slightly.\emph{Creeek} John made sure he shut the
door very firmly before opening the next one and slipping through it,
mind you he was carrying the girl, who was, luckily, still sleeping
through all of this!

No one was up still, seeing as it was the Blessing of the Clocktower
day. This is an annual day that happens every spring, so everyone has a
three hour lie in. John padded through the empty village, every now and
then glancing down at the beautiful girl who lay unconscious in his
tired arms.

``How long does it take you old-old-old person'' John's wife screeched.
John was still closing the door, he had his back to his wife and was
smiling smugly.

``What is it you ol-'' she stopped, ``You've found one ! Let's see!''.
John brought her over to the old lady lying in her rickety old bed.
``where, where did you find her? she said with a certain awe in her
croaky voice. John just tapped his nose suspiciously at he question.

``She's certainly a looker, let's put her to bed!'' John's wife, Doriene
said. So they tucked the girl up in the spare bed, turned out the light
and went into the kitchen, right out of ear shot.

``Doriene she had a neck chain'' John said inquiringly.

``Yes, go on.'' she said suspiciously.

``Well - it - there was a boy where I found her too. They both had
connecting love hearts, one (the one on the girls neck) said \emph{Oli}
and had an exact engravement of the boy and the other one (the one round
the boy's neck) had the name \emph{Pippa} engraved and an exact picture
of her!'' John said gulping at the end.

``Well who gives a damn about the boy? But the girl'' Doriene said
slowly, ``The girl, you mean to say, no you mean she's got a name!'' she
said excitedly.

``Yes, Pippa!'' John said.

``Phew! that saves us having to figure one out!'' she said relieved.

Pippa sat and the flopped back down again, but wait, the old oak tree
didn't make a disturbing creaking noise whenever you sit up. she lay
down in the hot, uncomfortable covers and gazed up at the ceiling. A
complicated network of spidery cracks that creep their way through the
dishevelled plaster. Pippa didn't understand, she didn't understand
anything. Why was she here? Why was the place so dismal? She looked down
at her chest, luckily the chain was still there, it was the only thing
she owned, except her straw hat and she loved them both. She knew the
hat was still on here head, she could feel it. Pippa sat up and the bed
made another freaky screech. She looked mournfully down at the broken
heart, and it reminded her how broken her's was. Tears started swelling
in her ocean blue eyes, they rolled away, down her cheek just like Oli
had done, she hoped he would come to this queer place any day and fetch
her from this prison. But Pippa wasn't one of those girls who expect
their prince to fetch them and waste away their days waiting for them.

Pippa decided to get out of this horrid bed and go and explore. She
didn't know what house this was or anything so she opened the door and
tried to be merry even though she was in a black hole of emotional
agony.

``Hello!'' Pippa said to the jostling village folks. They murmured and
whispered, Pippa guessed they were shocked that a new person was here.
But everyone smiled and Pippa over heard some old lady say to another
``She's ours Miranda, John found her, he won't say where though!''

``Personally Doriene I think she's lovely, and that old John's been
searching for donkey's years!'' Miranda replied.

Pippa skipped past all the houses until she came to the Clock Tower.
Everything was the same, ordinary and generally boring, except the Clock
Tower. It loomed over everybody as though it was a god watching over
everybody.

Just then Pippa heard a man say something about her, he mentioned her
name. She spun round and looked thoughtfully at him. He said to another
old man that she was called Pippa, \emph{tick} and he said she was
\emph{his} \emph{cross!} The other man said something like ``Nice find
John''. Aha! It all fitted the old lady, Doriene, said that John had
found Pippa and this man was called John, so they were husband and wife!

Pippa's honey coloured hair trickled like a lake of caramel in the light
breeze. Her eyes shone just like a rare stone in the sunshine.

Everybody stopped and stared at the girl who John and Doriene had
claimed was their foundling as she gazed up at the village's pride and
glory. The Clock Tower.

Months past and the whole village adored Pippa, yet she always,
secretly, in her forever broken heart, longed to go back home, where
everything is a story and a fairy tale. You see, where Pippa used to
live was a book. she is a fairy tale, a character from a child's bedtime
story, so she will never grow up in the human world.

The past few months Pippa had been sleeping in the ramshackle house with
John and Doriene, they treated her as though she was their child, Pippa
didn't mind really but she cried sorrowfully every night.

On one very unexpected day news came around, and first to Pippa seeing
as she lived with them, that Doriene, after all these years was
pregnant. As soon as John and Doriene knew they despised Pippa
immediately. They banished her from their home and Pippa huddled up in
the town square at night shivering and weeping more than ever. She
couldn't bare it here any longer, but she had to.

Months grew by and John and Doriene got more evil. Years and they got
worse, their baby, who they named Melificent, grew and grew and when she
was old enough to understand that Pippa was the village sweetheart she,
like her parents, loathed her with all her hatred.

Melificent was the same age as pippa now, because as I said Pippa never
grows up. She had long jet black hair and dark scowling raven's eyes,
which were quite a contrast with Pippa's turquoise, marine blue ones.
Melificent always wore black or grey. Pippa thought this shows her mood
a lot of the time, but she'd never such a thing out loud. Pippa always
wore the same bright coloured dress with sea blue embroidered flowers
and butterflies on and a lilac patterned hem.

It was spring in the village and everyone was preparing for the Annual
Blessing of the Clock Tower, which was taking place tomorrow. Everyone
was hustling and jostling preparing great meals, practising performances
for the great banquet, and sewing new dresses and stitching suits for
the men, some were rehearsing speeches fro the ceremony and others were
putting up banners.

Pippa was helping decorate the marquee with posies of gorgeous flowers
and laying candles out on the picnic tables when a bony finger tapped
her on the shoulder. She turned round to see Melificent smiling fakely
at her. She was wearing a dark dress that trailed after her like a
wedding dress except much more sinister and gloomy.

``Hello Melificent!'' Pippa said trying not to sound like she was
dreading what Melificent was about to say.

``I have a present for you'' she said in her sharp forceful voice, yet
this time there an was an element of kindness in there somewhere. Pippa
trailed after her, trying not to step on her extravagant train.

When they reached Melificent's house the door was opened abruptly she
didn't even knock. John was standing in the doorway, he smiled politely
and Pippa smiled back but she saw a glint of excitement in his eyes, but
then it vanished. Melificent showed her through to the living room. She
gestured to Pippa to sit on one of the faded couches. Pippa did, it
squeaked as she did so. At this point Pippa was a bit puzzled. Why would
Melificent, of all people, give her mortal enemy a surprise present? At
that moment John came in holding a cone shaped parcel wrapped in brown
paper. John and Melificent exchanged glances, Pippa couldn't tell what
they were so merry and smiley about. She could not understand why. She
was starting o get suspicious.

``Here, open it Pips'' Melificent said too kindly to be true. So Pippa
started to unwrap the massive parcel. She began to see something red and
she touched it, it was soft and it felt like the most expensive velvet
in the whole village!

Pippa did as she was told and slipped on the amazing dress for size. It
fitted her perfectly. She loved it but she knew something just wasn't
right.

John and Melificent told her to wear it tomorrow, they said that they
would keep it safe until then.

The next day everybody had a three hour lie in and then got up all merry
and excited. People did the last finishing touches to the marquee and
then went back home to get dressed up.

``Aah Pippa!'' a kind voice came from behind her.

``Oh hello Melificent!'' she said trying to sound delighted.

``Come on, lets go and dress you up!'' Melificent said as though Pippa
was her dolly.

Melificent was already dressed up in a floating frock with puffed
sleaves and silver embroidery on the collar and hem. Her hair was
scraped back into a tight knot at the top of her head.

``Come in you two!'' Doriene said warmly, yet she looked somewhat
troubled just the same. They all sat down in the living room and John
fetched the dress from Melificent's room.

``Would you like to change in darling Melificent's room, dear?'' Doriene
said with an air of excitement in her voice. Pippa changed into the
velvet dress, something was different though, the dress was still velvet
and it still had the satin ribbon round the waist, but it felt slightly
heavier. Pippa looked down. ``Oh, we attached a new hem dear'' John said
because he had seen her look down.

``Yes, we thought the other one was a bit to normal!'' Melificent said
quickly. So they tied Pippa's hair in a bun and wrapped the matching
ribbon on that they had also given her and she slipped on the tiny
ballet pumps and they all went to do the blessing of the Tower.

The Blessing of the Tower is where every family in the village goes up
the extremely long staircase and looks out the Clock Tower window. The
rest of the village cry the words ``Bless he Clock Tower and the People
for ever more''.

This year John and his family had said they would all go up together.
Pippa agreed but every minute Pippa's suspicion was rising. They had all
despised her since the day Melificent was born! Why were they suddenly
doling out presents and considering her one of the family again? Pippa
thought.

After almost every family had walked up the terrific staircase and made
their wish it was a little orphan boy's turn, Kit he was called. He ran
right up the stairs, so eager to make his wish, Kit popped his had out
of the window and looked down at the village below, practically specs so
hard to see. They all chanted the same words, then Kit had to make a
wish, most people wished for gold or riches. They rarely came true, he
thought, because nothing exciting ever happens in this village. Kit
closed his eyes and wished. He wished deep down in his heart to be able
to put something right when it was about to go wrong.

After Kit it was John, Doriene, Melificent and Pippa's turn. They all
padded up the tiring staircase and looked out the already open window.
Melificent probably wished for new dresses, Doreine probably wished for
new knitting needles and John, well who knows! But when it came to
Pippa's turn she wished and hoped with all her soul that one day she
would return to Oli and where she used to live.

Then something very peculiar happened. Everyone stopped putting on their
fake smiles and kindness and Melificent pursed her lips and scowled,
John frowned and Doriene looked spitefully at pippa again. Melificent
whipped out a matching blood red velvet strip and she tied it firmly
round Pippa's mouth ``Otoffmmblur hulp!'' Pippa tried to scream but
failing. Then John lifted Pippa's light body into a gap in the cog works
and Pippa began twisting and turning, spinning and whirling, she
couldn't stop!

``The gag matches the dress!'' Melificent said smiling, they all turned
and walked down the spiral staircase. Pippa watched her life slip away
for she knew that if the clock tower didn't chime the whole village
would freeze and go grey, so she was trapped swirling in this prison,
she was a cog just a hopeless, lifeless cog. She realised what a fool
she had been falling into their trap and now she was in a life prison
never to see the light of day again.

By the time Melificent, John and Doriene came down everyone was already
tucking into the marvellous banquet and those who weren't quite there
yet didn't count how many people came down from the Clock Tower, except
one: Kit.

Oli was sitting head in hands crying his way through the night. He asked
the Elves (who were the only ones still awake at midnight) for the
trillionth time to swear on their soul that they didn't tell \emph{any}
one where Pippa slept.

Oli had gone on a diet of leaves and all the types of berries that
people usually avoid since Pippa left. It had been fifteen years since,
yet every day and every night he made the Elves swear on their lives
they hadn't seen anyone take her. Of course they said no, but they were
lying through their coffee coloured teeth.

Oli decided he was going to go for a midnight stroll. He went to where
he and Pippa used to gaze at the clouds, on the hillside.

When he got there Oli spotted something he hadn't ever seen before: a
door. Oli went to investigate. He managed to yank it open. It was dark
in here too but it was an enclosed space with wooden walls. In front of
him Oli saw another set of doors. He pulled them both open. It wasn't
night here, it was about midday and he saw lots of people gathered in a
big marquee tent. Bunting hung all around and Oli realised he had just
stepped out of a Clock Tower.

Oli went over to a boy of about eight and he was reading a fairytale
book.

``Excuse me?'' Oli said politely.

``Hello!'' the boy said back ``I'm Kit, who are you?'' he said.

``Oli! Nice to meet you'' Oli replied ``Have you seen or heard of a girl
called Pippa?'' he said.

``Yes'' Kit said in a more hushed tone ``I'm the only one who knows this
but she is in the Clock Tower!'' Kit whispered. ``Come on'' Kit said and
showed Oli through and up some stairs that Oli had not noticed.

When they reached the top Oli stopped and gauped and then cried
``Pippi!''.

``Oli!'' the twirling girl shrieked. Pippa was dancing ballet and
couldn't stop. She explained to Oli about how the Clock Tower powered
the village so he, Kit and dancing Pippa made a plan of action. They
would quickly swap Pippa for the other cog that lay forgotten in the
corner and then they would go down and get Melificent and John and
Doriene arrested and sent away.

So they switch pippa for the cog and rushed down the staircase. The
three burst through the double doors and Kit cried ``John, Melificent,
Doriene you are under arrest!'' Everyone turned round and John,
Melificent and Doriene were lost for words. A little orphan was claiming
them under arrest, but they knew full well why. Some police officers
came and handcuffed all three and they were shipped off somewhere not so
nice.

Oli and Pippa asked Kit whether he would like to come home with them, he
agreed. So Pippa, Oli and Kit lived as you might say \emph{\emph{Happily
Ever After}}
